### 2018-08-08 paper/casestudies.tex
Theorem on trace refinement testing added
small improvements

% =======================================================================
\subsection{Testing for Trace Equivalence}

@@

% =======================================================================
\subsection{Testing for Failures Equivalence}

@@

>>>>

@@

@@

For implementing the test case $U_F(p)$ with sub-processes $U_F(p,s)$, 
it is advisable to avoid an enumeration
of traces $s$ the reference process has run through. Instead, we calculate
the following auxiliary functions from $P$'s transition graph.
\begin{eqnarray*}
\text{initials} & : & N \fun \power (\Sigma) 
\\
\text{minHit} & : & N \fun \power\power(\Sigma)
\end{eqnarray*}
In a state $n = G(P)/s$, the set $\text{initials(n)}$ equals the events labelling
outgoing edges of $n$, so  $\text{initials(n)} = [P/s]^0$. Function $\text{minHit}$
maps $n$ to the set of all minimal hitting sets associated with the minimal acceptances
of $n$, so $\text{minHit}(n) = \text{minHit}(P/s)$. Then, using the transition function
of $t$ in addition to the two auxiliary functions, $U_F(p)$ can be re-written
as the failures-equivalent CSP process
\begin{eqnarray}
U_F^1(p) & = & U_F^1(p,0,\ii n)
\\
U_F^1(p,k,n) & = & \big( e:(\Sigma - \text{initials}(n)) \then \efail\then \Stop \big)
\label{eq:xufa}
\\ & & \extchoice \nonumber
\\ & & (\text{initials}(n) = \varnothing)    \&   \big( \epass \then \Stop \big)
\label{eq:xufb}
\\ & & \extchoice \nonumber
\\ & & (k < p) \& \big( e:\text{initials}(n) \then U_F^1(p,(k+1),t(n,e)) \big)
\label{eq:xufc}
\\ & & \extchoice \nonumber
\\ & & (k = p) \& \big( \sqcap_{H\in\text{minHit}(n)} ( e:H \then \epass \then\Stop   )  \big)
\label{eq:xufd}
\end{eqnarray}

\begin{example}
\label{ex:uf1tests}

\end{example}

### 2018-08-08 paper/preliminaries.tex
small improvements

\begin{example}\label{ex:a}
Consider the CSP process $P$ defined below, and that the set of events
$\Sigma$ is $\{a,b,c\}$.
\begin{eqnarray*}
P & = & a \then (Q\intchoice R)
\\
Q & = & a \then P \extchoice c \then P
\\
R & = & b \then P \extchoice c \then R
\end{eqnarray*}
Its transition graph $G(P)$ is shown in Fig.~\ref{fig:tga}. Process state
$P/\langle\rangle$ is represented there as Node\_0, with $\{ b,c\}$ as the
only maximal refusal, since $a$ can never be refused, and no other events are
accepted. Having engaged into $a$, the transition emanating from Node\_0
leads to Node\_2 representing  the process state $P/a = Q\intchoice R$. The
internal choice operator induces several refusal sets derived from $Q$ and
$R$. Since these processes accept their initial events in external choice,
$Q\intchoice R$ induces two maximal refusal sets $\{b\}$ and
$\{a\}$. Note that event $c$ can never be refused, since it is not a member
of any maximal refusal.

Having engaged into $c$, the next process state is represented by Node\_1.
Due to normalisation, there is only a single transition satisfying
$t(\text{Node\_2},c) = \text{Node\_1}$. This transition, however, can have
been caused by either $Q$ or $R$ engaging into $c$, so Node\_1 corresponds to
process state $Q/c \intchoice R/c = P \intchoice R$. This is reflected by the
two maximal refusals labelling Node\_1.

Similar considerations explain the other nodes and transitions in
Fig.~\ref{fig:tga}.

Note that the node names including their number suffixes 
are generated by the FDR tool (see next paragraph).
The numbering is generated   during the normalisation procedure.
Therefore, the node numbers do not reflect the distance from the initial node
Node\_0.
\end{example}

@@

\begin{lemma}
\label{lemma:tgtrcref}
\begin{eqnarray}
P \lessdet_T Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P))
\label{eq:trcrefa}
\\
\label{eq:failrefa}
P \lessdet_F Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P)) \wedge {} \nonumber
\\ & & \forall s\in\trc(G(Q)), R_Q\in\maxrefs(G(Q)/s):  \nonumber
\\ & & \tabd
\exists R_P\in\maxrefs(G(P)/s): R_Q\subseteq R_P
\\
\label{eq:failrefb}
P \lessdet_F Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P)) \wedge {} \nonumber
\\ & & \forall s\in\trc(G(Q)), A_Q\in\minaccs(G(Q)/s): \nonumber
\\ & & \tabd
\exists A_P\in\minaccs(G(P)/s): A_P\subseteq A_Q
\end{eqnarray}
\end{lemma}

For proving our main theorems, it is necessary to consider the \emph{product} of 
normalised transition graphs. We need this only for the investigation of corresponding traces in reference processes and processes under test. Therefore, the 
labelling of nodes with maximal refusals or minimal acceptances   will be disregard in the 
product construction.
Consider two normalised transition graphs 
\[
G_i = ( N_i, \ii n_i, \Sigma, t_i : N_i\times\Sigma \pfun N_i, r_i : N_i \fun \mathbb{P}\mathbb{P}(\Sigma)),\qquad i = 1,2,
\]
over the same alphabet $\Sigma$. Then their product is defined by
\begin{eqnarray}
G_1\times G_2 & = & (N_1\times N_2,(\ii n_1,\ii n_2), t:(N_1\times N_2)\times\Sigma\pfun (N_1\times N_2))
\\
\dom~t & = & \{ ((n_1,n_2),e)\in (N_1\times N_2)\times\Sigma~|   \nonumber
\\ & & \tabc
(n_1,e)\in\dom~t_1\wedge 
(n_2,e) \in\dom~t_2    \}
\\
t((n_1,n_2),e) & = & (t_1(n_1,e),t_2(n_2,e))\ \text{for $((n_1,n_2),e)\in\dom~t$}
\end{eqnarray}

>>>>

\begin{example}\label{ex:a}
Consider the CSP process $P$ defined below, and that the set of events
$\Sigma$ is $\{a,b,c\}$.
\begin{eqnarray*}
P & = & a \then (Q\intchoice R)
\\
Q & = & a \then P \extchoice c \then P
\\
R & = & b \then P \extchoice c \then R
\end{eqnarray*}
Its transition graph $G(P)$ is shown in Fig.~\ref{fig:tga}. Process state
$P/\langle\rangle$ is represented there as Node\_0, with $\{ a\}$ as the
only minimal acceptance, since $a$ can never be refused, and no other events are
accepted. Having engaged into $a$, the transition emanating from Node\_0
leads to Node\_2 representing  the process state $P/a = Q\intchoice R$. The
internal choice operator induces several minimal acceptances derived from $Q$ and
$R$. Since these processes accept their initial events in external choice,
$Q\intchoice R$ induces minimal acceptance sets $\{a,c\}$ and
$\{b,c\}$. Note that event $c$ can never be refused, since it is contained in each minimal acceptance set.

Having engaged into $c$, the next process state is represented by Node\_1.
Due to normalisation, there is only a single transition satisfying
$t(\text{Node\_2},c) = \text{Node\_1}$. This transition, however, can have
been caused by either $Q$ or $R$ engaging into $c$, so Node\_1 corresponds to
process state $Q/c \intchoice R/c = P \intchoice R$. This is reflected by the
two minimal acceptance sets labelling Node\_1.
Similar considerations explain the other nodes and transitions in
Fig.~\ref{fig:tga}.

Note that the node names including their number suffixes 
are generated by the FDR tool (see next paragraph).
The numbering is generated   during the normalisation procedure.
Therefore, the node numbers do not reflect the distance from the initial node
Node\_0.
\xbox
\end{example}

@@

\begin{lemma}
\label{lemma:tgtrcref}
\begin{eqnarray}
P \lessdet_T Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P))
\label{eq:trcrefa}
\\
\label{eq:failrefa}
P \lessdet_F Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P)) \wedge {} \nonumber
\\ & & \forall s\in\trc(G(Q)), R_Q\in\maxrefs(G(Q)/s):  \nonumber
\\ & & \tabd
\exists R_P\in\maxrefs(G(P)/s): R_Q\subseteq R_P
\\
\label{eq:failrefb}
P \lessdet_F Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P)) \wedge {} \nonumber
\\ & & \forall s\in\trc(G(Q)), A_Q\in\minaccs(G(Q)/s): \nonumber
\\ & & \tabd
\exists A_P\in\minaccs(G(P)/s): A_P\subseteq A_Q
\end{eqnarray}
\xbox
\end{lemma}

For proving our main theorems, it is necessary to consider the \emph{product} of 
normalised transition graphs. We need this only for the investigation of corresponding traces in reference processes and processes under test. Therefore, the 
labelling of nodes with maximal refusals or minimal acceptances   will be disregarded in the 
product construction.
Consider two normalised transition graphs 
\[
G_i = ( N_i, \ii n_i, \Sigma, t_i : N_i\times\Sigma \pfun N_i, r_i : N_i \fun \mathbb{P}\mathbb{P}(\Sigma)),\qquad i = 1,2,
\]
over the same alphabet $\Sigma$. Then their product is defined by
\begin{eqnarray}
G_1\times G_2 & = & (N_1\times N_2,(\ii n_1,\ii n_2), t:(N_1\times N_2)\times\Sigma\pfun (N_1\times N_2))
\\
\dom~t & = & \{ ((n_1,n_2),e)\in (N_1\times N_2)\times\Sigma~|   \nonumber
\\ & & \tabc
(n_1,e)\in\dom~t_1\wedge 
(n_2,e) \in\dom~t_2    \}
\\
t((n_1,n_2),e) & = & (t_1(n_1,e),t_2(n_2,e))\ \text{for $((n_1,n_2),e)\in\dom~t$}
\end{eqnarray}
